Reducing Acceptance Marks in Emerson-Lei Automata by QBF Solving

### 2023-06-02 paper/main.tex
polishing in Table 1

\begin{table}[t]
  \caption{Considered LTL to automata translators and the numbers of
    fails and successfully constructed automata with at most one mark and with at least two marks for each translator and set of
    formulas.}
\label{tab:ltltranslators}
\centering
% \begin{tabular}{lr@{~~~~~~}lr}
% \toprule
% tool        & version&homepage & ~~~automata \\
% \midrule
% \texttt{ltl2dela}~~~ & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 129\\
% \texttt{ltl2dgra} & 21.0 & & 234\\
% \texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 70\\
% \texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} & 91\\
% \bottomrule
% \end{tabular}
%
% \begin{tabular}{lrrrr}
%   \toprule
%   &&& \multicolumn{2}{c}{constructed automata with} \\ \cmidrule(lr){4-5}
%   tool &\!\!\!version/homepage & ~~~~fails & less than 2 marks & \textbf{at least 2 marks}\\
%   \midrule
%   \texttt{ltl2dela} & 21.0\tablefootnote{\label{fn:owl}\url{https://owl.model.in.tum.de/}}
%        & 5 & 214 & \textbf{129} \\
%   \texttt{ltl2dgra} & 21.0\footnotemark[1]
%        & 12 & 102 & \textbf{234}\\
%   \texttt{ltl2tgba} & 2.10.4\tablefootnote{\url{https://spot.lrde.epita.fr}}
%        & 0 & 278 & \textbf{70}\\
%   \texttt{ltl3tela} & 2.2.0\tablefootnote{\url{https://github.com/jurajmajor/ltl3tela}}
%        & 18 & 239 & \textbf{91}\\
%   \bottomrule
% \end{tabular}
%

\setlength{\tabcolsep}{5.7pt}
\begin{tabular}{lrrrrrrr}
  \toprule
  && \multicolumn{3}{c}{\!348 formulas from literature\!} & \multicolumn{3}{c}{366 random formulas}\\
  \cmidrule(lr){3-5} \cmidrule(lr){6-8}
  &&& \multicolumn{2}{c}{automata with} && \multicolumn{2}{c}{automata with}\\
  \cmidrule(lr){4-5} \cmidrule(lr){7-8}
  &&& at most & \textbf{at least} && at most & \textbf{at least}\\[-.8ex]
  \multicolumn{2}{l}{translator ~~~ (version)$^{\text{web}}$} & ~~~~fails & 1 mark & \!\!\!\!\textbf{2 marks} & ~~~~fails & 1 mark & \!\!\!\!\textbf{2 marks}\\
  \midrule 
  \texttt{ltl2tgba -G} & (2.10.4)\tablefootnote{\url{https://spot.lrde.epita.fr}}
  & 0 & 278 & \textbf{70} & ? & ? & \textbf{?}\\
  \texttt{ltl3tela} & (2.2.0)\tablefootnote{\url{https://github.com/jurajmajor/ltl3tela}}
  & 18 & 239 & \textbf{91} & ? & ? & \textbf{?}\\
  \texttt{ltl3tela -D1} & (2.2.0)\tablefootnote{\url{https://github.com/jurajmajor/ltl3tela}}
  & ? & ? & \textbf{?} & ? & ? & \textbf{?}\\ 
  \texttt{ltl2dela} & (21.0)\tablefootnote{\label{fn:owl}\url{https://owl.model.in.tum.de/}}
       & 5 & 214 & \textbf{129} & ? & ? & \textbf{?} \\
  \texttt{ltl2dgra} & (21.0)\footnotemark[4]
       & 12 & 102 & \textbf{234} & ? & ? & \textbf{?}\\
  \bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[t]
  \caption{Considered translators and the numbers of \emph{fails} and
    successfully constructed automata with \emph{at most 1 mark} and
    with \emph{at least 2 marks} for each translator and set of
    formulas.}
\label{tab:ltltranslators}
\centering
% \begin{tabular}{lr@{~~~~~~}lr}
% \toprule
% tool        & version&homepage & ~~~automata \\
% \midrule
% \texttt{ltl2dela}~~~ & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 129\\
% \texttt{ltl2dgra} & 21.0 & & 234\\
% \texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 70\\
% \texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} & 91\\
% \bottomrule
% \end{tabular}
%
% \begin{tabular}{lrrrr}
%   \toprule
%   &&& \multicolumn{2}{c}{constructed automata with} \\ \cmidrule(lr){4-5}
%   tool &\!\!\!version/homepage & ~~~~fails & less than 2 marks & \textbf{at least 2 marks}\\
%   \midrule
%   \texttt{ltl2dela} & 21.0\tablefootnote{\label{fn:owl}\url{https://owl.model.in.tum.de/}}
%        & 5 & 214 & \textbf{129} \\
%   \texttt{ltl2dgra} & 21.0\footnotemark[1]
%        & 12 & 102 & \textbf{234}\\
%   \texttt{ltl2tgba} & 2.10.4\tablefootnote{\url{https://spot.lrde.epita.fr}}
%        & 0 & 278 & \textbf{70}\\
%   \texttt{ltl3tela} & 2.2.0\tablefootnote{\url{https://github.com/jurajmajor/ltl3tela}}
%        & 18 & 239 & \textbf{91}\\
%   \bottomrule
% \end{tabular}
%

\setlength{\tabcolsep}{5.7pt}
\begin{tabular}{lrrrrrrr}
  \toprule
  && \multicolumn{3}{c}{\!348 formulas from literature\!} & \multicolumn{3}{c}{366 random formulas}\\
  \cmidrule(lr){3-5} \cmidrule(lr){6-8}
  &&& \multicolumn{2}{c}{automata with} && \multicolumn{2}{c}{automata with}\\
  \cmidrule(lr){4-5} \cmidrule(lr){7-8}
  &&& at most & \textbf{at least} && at most & \textbf{at least}\\[-.8ex]
  \multicolumn{2}{l}{translator ~~~ (version)$^{\text{web}}$} & ~~~~fails & 1 mark & \!\!\!\!\textbf{2 marks} & ~~~~fails & 1 mark & \!\!\!\!\textbf{2 marks}\\
  \midrule 
  \texttt{ltl2tgba -G} & (2.10.4)\tablefootnote{\url{https://spot.lrde.epita.fr}}
  & 0 & 278 & \textbf{70} & ? & ? & \textbf{?}\\
  \texttt{ltl3tela} & (2.2.0)\tablefootnote{\url{https://github.com/jurajmajor/ltl3tela}}
  & 18 & 239 & \textbf{91} & ? & ? & \textbf{?}\\
  \texttt{ltl3tela -D1} & (2.2.0)\footnotemark[2]
  & ? & ? & \textbf{?} & ? & ? & \textbf{?}\\ 
  \texttt{ltl2dela} & (21.0)\tablefootnote{\label{fn:owl}\url{https://owl.model.in.tum.de/}}
       & 5 & 214 & \textbf{129} & ? & ? & \textbf{?} \\
  \texttt{ltl2dgra} & (21.0)\footnotemark[3]
       & 12 & 102 & \textbf{234} & ? & ? & \textbf{?}\\
  \bottomrule
\end{tabular}
\end{table}
